What should I notice? Evaluating the memorability of events for abductive inference.

### 2021-10-14 new_paper.tex
Added conclusion, the two examples, and some other minor corrections

\textbf{TODO:} Mettre un passage ici pour dire que ça résoud le dilemne de la récence présenté dans l'intro

@@

\subsection{Results}
\label{sec:example}
\subsubsection{Memorability}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{figures/complexities_computed}
    \caption{Computed description complexities of events with retrieval paths of
        length at most 4. Events of type ``day'' (blue), ``hot'' (green), ``cold''
        (red), ``device removal''(cyan) are shown.}
    \label{fig:computed_cplx}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{figures/complexities_surprises}
    \caption{Memorability score for events in memory}
    \label{fig:result1}
\end{figure}

Given that we generated the data used for this experiment, it is possible to
flag all perturbation events from the usual daily events and evaluate how a
detection based on ``memorability'' score would perform in distinguishing these
events. The result is presented as a ROC curve in Figure \ref{fig:roc}.

\textbf{TODO:} Il faudrait commenter la courbe
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{./figures/roc}
    \caption{Experimental ROC curve (True Positive Rate against False Positive
        Rate) for a classifier based on our memorability score. Measures consider 23
        manually flagged events as memorable (events added to the normal background
        as described in Section~\ref{sec:example}.)}
    \label{fig:roc}
\end{figure}
\subsubsection{Abduction}

To show the potential application to abductive inference, we use our approach to the first scenario, to see if memorabilty alone can find the brand new TV to be a reasonable cause for the sudden low light.

\begin{figure}
    \centering
    \includegraphics[width=.8\linewidth]{./figures/abduction_1_results}
    \caption{Outputs of the memorability-based abduction module. This represent the 3 events in the memory having the highest memorability score relative to the consequence event.}
    \label{fig:abduction_res}
\end{figure}

As an illustration of the abductive inference made possible our memorability
score, we used as a target anomaly the temperature drops visible in the raw
time series data from our scenario (fig \ref{fig:ts_example}).

@@

\subsection{Perspectives}
\label{sec:future}
The main purpose of the present paper is to show the possible connections
between existing definitions of simplicity from cognitive science, Algorithmic
Information Theory and a practical use case in cyber-physical systems. As such,
many further improvements can be done to pave the way towards a better
integration and performance for anomaly detection or abduction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
The introduction of description complexity and the subsequent memorability measure allows to compare events of various types with different characteristics. As such, it provides a framework to discriminate peculiar events and outliers.

>>>>

@@

\subsection{Results}
\label{sec:example}

\subsubsection{The ``TV'' scenario:}
\paragraph{Memorability}
The computation of the description complexity measure for the 2400 events recorded in this scenario took around 90 seconds using an i7-8600u laptop. The resulting complexities, in Figure \ref{fig:scenar1_complexity}, clearly shows that TV events appear more simple than luminosity events. In fact, for most luminosity events, the complexity corresponds to the random choice complexity, 25 bits in this example. This pattern comes from the number of luminosity events per day, 24, is too high to consider the retrieval path $day(k) \rightarrow randomPick()$ simpler than $randomPick$ from the entire memory, except for the first more recent days, which appear simpler (on the right-hand side of Figure \ref{fig:scenar1_complexity})
\begin{figure}
    \centering
    \includegraphics[width=.7\linewidth]{figures/memorability_scenar_1.png}
    \caption{Description complexity for events recorded in the TV scenario. Luminosity events are shown in blue, TV events in green}
    \label{fig:scenar1_complexity}
\end{figure}
\paragraph{Abduction}
To show the potential application to abductive inference, we use our approach to the first scenario, to see if memorabilty alone can find the brand new TV to be a reasonable cause for the sudden low light.

\begin{figure}
    \centering
    \includegraphics[width=.8\linewidth]{./figures/abduction_1_results}
    \caption{Outputs of the memorability-based abduction module. This represent the 3 events in the memory having the highest memorability score relative to the consequence event.}
    \label{fig:abduction_res}
\end{figure}
\subsubsection{The ``temperature'' scenario:}
\paragraph{Memorability}

@@

\begin{figure}[ht]
    \centering
\includegraphics[width=.8\linewidth]{figures/complexities_computed}
    \caption{Computed description complexities of events with retrieval paths of
length at most 4. Events of type ``day'' (blue), ``hot'' (green), ``cold''
(red), ``device removal''(cyan) are shown.}
    \label{fig:computed_cplx}
\end{figure}

@@

\begin{figure}[ht]
    \centering
\includegraphics[width=.8\linewidth]{figures/complexities_surprises}
    \caption{Memorability score for events in memory}
    \label{fig:result1}
\end{figure}

Given that we generated the data used for this experiment, it is possible to
flag all perturbation events from the usual daily events and evaluate how a
detection based on ``memorability'' score would perform in distinguishing these
events. The result is presented as a ROC curve in Figure \ref{fig:roc}. This shows the memorability score's performance as a classifying tool for ``out-of-the norm'' events. In this example, memorability alone correctly identified 18 manually generated events with only 2 false-positives. While the direct application of memorability for classification or event detection is not within the scope of this paper (see Section \ref{sec:related} for complexity-based detection), this first result is on par with the motivation of memorability being in accordance with the intuitive notion.

\begin{figure}[ht]
    \centering
\includegraphics[width=0.7\linewidth]{./figures/roc}
    \caption{Experimental ROC curve (True Positive Rate against False Positive
Rate) for a classifier based on our memorability score. Measures consider 23
manually flagged events as memorable (events added to the normal background
as described in Section~\ref{sec:example}.)}
    \label{fig:roc}
\end{figure}
\subsubsection{Abduction}

\paragraph{Abduction}
As an illustration of the abductive inference made possible our memorability
score, we used as a target anomaly the temperature drops visible in the raw
time series data from our scenario (fig \ref{fig:ts_example}).

@@

\subsection{Perspectives}
\label{sec:future}

% L'utilisation d'une mesure unique de la mémorabilité d'événements de natures et caracteristiques diverses 
% La mise en application pratique des notions théoriques de mémorabilité et mémorabilité relative nécessité des développements futurs. Dans cette section, nous en avons sélectionné 2 qui nous semblent, à ce jour, les plus préoccupants.
The practical application of the theoretical notions of memorability and relative memorability requires future developments. In this section, we have selected two of them which seem to us, to date, the most challenging.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
The introduction of description complexity and the subsequent memorability measure allow to compare events of various types with different characteristics. As such, it provides a formal and generic framework to discriminate peculiar events and outliers.
